Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-27 paper/paper.tex
A lot of revisions; still working on the figure text/layout

\begin{figure}
\begin{center}
 \begin{tikzpicture}
   \matrix (m) [matrix of math nodes, row sep=2.5em, column sep=3.7em]
     {
         &  &  &  &
       \begin{smallmatrix} \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
       \begin{smallmatrix} \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
       \begin{smallmatrix} \text{disentangled}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{refunctionalized}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{monadic} \\ \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix}  \\
       \begin{smallmatrix} \text{abstract} \\ \text{machines} \end{smallmatrix} &
         &
       %\begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
         &
       %\begin{smallmatrix} \text{disentangled} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
         &
       %\begin{smallmatrix} \text{refunctionalized} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
     };
   {
     [start chain] \chainin (m-2-4);
     \chainin (m-1-5) [double,join={node[sloped,anchor=center,above,labeled] {\text{CPS left-inv.}}}];
     \chainin (m-2-5) [join={node[above,labeled] {\text{}}}];
     \chainin (m-1-5) [join={node[above,labeled] {\text{}}}];
   }
   %{ [start chain] \chainin (m-1-5);
   % \chainin (m-2-4) [join={node[sloped,anchor=center,above,labeled] {\text{CPS trans.}}}]; }
   %
   % TODO: find out how to make the arrows visually separate
   % {
   %   [start chain] \chainin (m-1-5);
   %   \chainin (m-2-4) [bend left=5, join={node[sloped,anchor=center,below,labeled] {\text{CPS}}}];
   % }
   {
     [start chain] \chainin (m-2-1);
     \chainin (m-2-2) [join={node[above,labeled] {\begin{smallmatrix} \text{linearization} \\ \text{+} \\ \text{fusion} \end{smallmatrix}}     }];
     \chainin (m-2-3) [join={node[above,labeled] {\text{disentang.}}}];
     \chainin (m-2-4) [join={node[above,labeled] {\text{refunc.}}}];
     %\chainin (m-2-5) [join={node[above,labeled] {\text{monadify}}}];
   }
   {
     [start chain, color=gray]
     \chainin (m-3-1);
     { [start branch=A] \chainin (m-2-1)
       [join={node[left, labeled] {\alpha}}];
     }
   }
     %\chainin (m-2-2);
     %\chainin (m-2-3);
     %\chainin (m-2-4);
   {
     [start chain, color=gray]
     \chainin (m-3-5);
     { [start branch=B] \chainin (m-2-5)
       [join={node[right, labeled] {\alpha}}];
     }
     {
       [start branch=D, color=gray] \chainin (m-3-1)
       [join={node[right, labeled] {\text{}}}];
     }
   }
   {
     [start chain, color=gray] \chainin (m-3-1);
     {
       [start branch=C] \chainin (m-3-5)
       [join={node[above, labeled] {\text{Known as Danvy's correspondences for concrete semantic artifacts }}}];
     }
   }
 \end{tikzpicture}
 \caption{Transformations from AAM to ADI} \label{fig:trans}
\end{center}
\end{figure}

@@

  \item Applying \textbf{refunctionalization} \cite{DANVY2009534, Danvy:2006:RW:2171265.2171268} 
    to disentangled AAM is shown in Section~\ref{sec:refunc}. 
    %as the left inverse of Reynolds' defunctionalization \cite{Reynold:72,Reynolds:HOSC98-revisited} 
    Refunctionalization replaces the first-order datatypes representing continuations with
    higher-order functions, and associates dispatching logic with proper higher-order functions. 
    We then derive an abstract interpreter written in continuation-passing style with two
    layers of continuations due to the nondeterminism.

>>>>

\begin{figure}
\begin{center}
 \begin{tikzpicture}
   \matrix (m) [matrix of math nodes, row sep=2.5em, column sep=3.7em]
     {
         &  &  &  &
       \begin{smallmatrix} \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
       \begin{smallmatrix} \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
       \begin{smallmatrix} \text{disentangled}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{refunctionalized}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{monadic} \\ \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix}  \\
       \begin{smallmatrix} \text{abstract} \\ \text{machines} \end{smallmatrix} &
         &
       %\begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
         &
       %\begin{smallmatrix} \text{disentangled} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
         &
       %\begin{smallmatrix} \text{refunctionalized} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
       \begin{smallmatrix} \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
     };
   {
     [start chain] \chainin (m-2-4);
     \chainin (m-1-5) [double,join={node[sloped,anchor=center,above,labeled] {\text{CPS left-inv.}}}];
     \chainin (m-2-5) [join={node[above,labeled] {\text{}}}];
     \chainin (m-1-5) [join={node[above,labeled] {\text{}}}];
   }
   %{ [start chain] \chainin (m-1-5);
   % \chainin (m-2-4) [join={node[sloped,anchor=center,above,labeled] {\text{CPS trans.}}}]; }
   {
     [start chain] \chainin (m-2-1);
     \chainin (m-2-2) [join={node[above,labeled] {\begin{smallmatrix} \text{linearization} \\ \text{+} \\ \text{fusion} \end{smallmatrix}}     }];
     \chainin (m-2-3) [join={node[above,labeled] {\text{disentang.}}}];
     \chainin (m-2-4) [join={node[above,labeled] {\text{refunc.}}}];
     %\chainin (m-2-5) [join={node[above,labeled] {\text{monadify}}}];
   }
   {
     [start chain, color=gray]
     \chainin (m-3-1);
     { [start branch=A] \chainin (m-2-1)
       [join={node[left, labeled] {\alpha}}];
     }
   }
     %\chainin (m-2-2);
     %\chainin (m-2-3);
     %\chainin (m-2-4);
   {
     [start chain, color=gray]
     \chainin (m-3-5);
     { [start branch=B] \chainin (m-2-5)
       [join={node[right, labeled] {\alpha}}];
     }
     {
       [start branch=D, color=gray] \chainin (m-3-1)
       [join={node[right, labeled] {\text{}}}];
     }
   }
   {
     [start chain, color=gray] \chainin (m-3-1);
     {
       [start branch=C] \chainin (m-3-5)
       [join={node[above, labeled] {\text{Known as Danvy's correspondences for concrete semantic artifacts }}}];
     }
   }
 \end{tikzpicture}
 \caption{Transformations from AAM to ADI} \label{fig:trans}
\end{center}
\end{figure}

@@

  \item Applying \textbf{Refunctionalization} \cite{DANVY2009534, Danvy:2006:RW:2171265.2171268} 
    to disentangled AAM is shown in Section~\ref{sec:refunc}. 
    %as the left inverse of Reynolds' defunctionalization \cite{Reynold:72,Reynolds:HOSC98-revisited} 
    Refunctionalization replaces the first-order datatypes representing continuations with
    higher-order functions, and associates dispatching logic with proper higher-order functions. 
    We then derive an abstract interpreter written in continuation-passing style with two
    layers of continuations due to the nondeterminism.
